Capstone Movielens Report

### 2025-12-06 reports/capstone-movielens.site/05.appendix.Rmd
Function described: train_UMGY_effect.cv.

::: {.noteblock data-latex=""}
In the above code snippet, the `calc_date_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv function) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
:::
:::

@@

#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) Function {#func.train_UMGY_effect.cv}
\

@@

@@

```{r eval=FALSE}
  cv.UMGY_effect <- train_UMGY_effect.cv()
```
:::

@@

@@

The most important part of the source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The complete source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) function is available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L61) script on _GitHub_.
:::
:::

>>>>

::: {.noteblock data-latex=""}
In the above code snippet, the `calc_date_general_effect.cv` function is called internally from the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function, along with the [calc_UMGY_effect](#func.calc_UMGY_effect) function (both described below).
:::
:::

@@

#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) Function {#func.train_UMGY_effect.cv}
\

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function (described below in section [UMGYE Model: Regularization] of *This Appendix*) as shown in the [Usage](#func.train_UMGY_effect.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

```{r eval=FALSE}
  train_UMGY_effect.cv(lambda) |>
    calc_UMGY_effect_RMSE.cv()
```

::: {.noteblock data-latex=""}
In the above code snippet, the `train_UMGY_effect.cv` function is called internally from the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYE Model: Regularization] section and *This Section*, respectively).
:::
:::

@@

Under the hood, this function internally calls the [calc_date_general_effect.cv](#func.calc_date_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in *This Section*).

@@

The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) function is shown below:
```{r eval=FALSE}
train_UMGY_effect.cv <- function(lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_effect.cv
`lambda` is `NA`")
  }

  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
}
```

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L3) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L86) script on _GitHub_.
:::
:::
